---
title: "CodeBook - Samsung Project"
author: "Tim Ferkel"
date: "3/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir=".//course3project")
```

## Study Design

Source data: [link]https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip  

The data extracted from the zip file consisted of training and testing data for 30 subjects performing 6 activities while wearing a Samsung phone on their waste.  The subjects were video taped and the activities being performed were manually captured.  Using the embedded gyroscope and accelerometer, the device recorded 3-axial linear acceleration and angular velocity at 50mHz.  From this data a feature set of 561 time and frequency domain variables was created for each activity/subject.  

The dataset includes the following files that are of interest for this project:  

File Name             Description  
-------------------   -------------------------------------------------------  
activity_labels.txt   Mapping of codes to activity  
features.txt          Names of the 561 variables  
subject_test.txt      Test set of subject recordings  
x_test.txt            Test record of 561 variables for each subject/activity  
y_test.txt            Test set of activities  
subject_train.txt     Train set of subject recordings  
x_train.txt           Train record of 561 variables for each subject/activity  
y_train.txt           Train set of activities

## Codebook  

When we look at the dimensions of the training files we find that they all have the same number of rows.  This infers that we can stitch them together to create a single dataframe representing all of the training data.


```{r} 
trainsubject<-read.table("subject_train.txt")
print(dim(trainsubject))
trainactivity<-read.table("y_train.txt")
print(dim(trainactivity))
trainmeasures<-read.table("x_train.txt")
print(dim(trainmeasures))
```
Of the 561 variables we are only interested in the ones that are a mean() or std(), of which there are 66 including:

Original variable name      Renamed Variable        Tidy Data Set Name            Summary     Units
-----------------------     --------------------    --------------------          --------    ------
tBodyAcc-mean()-X	          tbodyaccmeanx	          meanoftbodyaccmeanx           Average     m/s^2^
tBodyAcc-mean()-Y	          tbodyaccmeany	          meanoftbodyaccmeany           Average     m/s^2^
tBodyAcc-mean()-Z	          tbodyaccmeanz	          meanoftbodyaccmeanz           Average     m/s^2^
tBodyAcc-std()-X	          tbodyaccstdx	          meanoftbodyaccstdx            Average     m/s^2^
tBodyAcc-std()-Y	          tbodyaccstdy	          meanoftbodyaccstdy            Average     m/s^2^
tBodyAcc-std()-Z	          tbodyaccstdz	          meanoftbodyaccstdz            Average     m/s^2^
tGravityAcc-mean()-X	      tgravityaccmeanx	      meanoftgravityaccmeanx        Average     m/s^2^
tGravityAcc-mean()-Y	      tgravityaccmeany	      meanoftgravityaccmeany        Average     m/s^2^
tGravityAcc-mean()-Z	      tgravityaccmeanz	      meanoftgravityaccmeanz        Average     m/s^2^
tGravityAcc-std()-X	        tgravityaccstdx	        meanoftgravityaccstdx         Average     m/s^2^
tGravityAcc-std()-Y	        tgravityaccstdy	        meanoftgravityaccstdy         Average     m/s^2^
tGravityAcc-std()-Z	        tgravityaccstdz	        meanoftgravityaccstdz         Average     m/s^2^
tBodyAccJerk-mean()-X	      tbodyaccjerkmeanx	      meanoftbodyaccjerkmeanx       Average     m/s^2^
tBodyAccJerk-mean()-Y	      tbodyaccjerkmeany	      meanoftbodyaccjerkmeany       Average     m/s^2^
tBodyAccJerk-mean()-Z	      tbodyaccjerkmeanz	      meanoftbodyaccjerkmeanz       Average     m/s^2^
tBodyAccJerk-std()-X	      tbodyaccjerkstdx	      meanoftbodyaccjerkstdx        Average     m/s^2^
tBodyAccJerk-std()-Y	      tbodyaccjerkstdy	      meanoftbodyaccjerkstdy        Average     m/s^2^
tBodyAccJerk-std()-Z	      tbodyaccjerkstdz	      meanoftbodyaccjerkstdz        Average     m/s^2^
tBodyGyro-mean()-X	        tbodygyromeanx	        meanoftbodygyromeanx          Average     radians/s
tBodyGyro-mean()-Y	        tbodygyromeany	        meanoftbodygyromeany          Average     radians/s
tBodyGyro-mean()-Z	        tbodygyromeanz	        meanoftbodygyromeanz          Average     radians/s
tBodyGyro-std()-X	          tbodygyrostdx	          meanoftbodygyrostdx           Average     radians/s
tBodyGyro-std()-Y	          tbodygyrostdy	          meanoftbodygyrostdy           Average     radians/s
tBodyGyro-std()-Z	          tbodygyrostdz	          meanoftbodygyrostdz           Average     radians/s
tBodyGyroJerk-mean()-X	    tbodygyrojerkmeanx	    meanoftbodygyrojerkmeanx      Average     radians/s
tBodyGyroJerk-mean()-Y	    tbodygyrojerkmeany	    meanoftbodygyrojerkmeany      Average     radians/s
tBodyGyroJerk-mean()-Z	    tbodygyrojerkmeanz	    meanoftbodygyrojerkmeanz      Average     radians/s
tBodyGyroJerk-std()-X	      tbodygyrojerkstdx	      meanoftbodygyrojerkstdx       Average     radians/s
tBodyGyroJerk-std()-Y	      tbodygyrojerkstdy	      meanoftbodygyrojerkstdy       Average     radians/s
tBodyGyroJerk-std()-Z	      tbodygyrojerkstdz	      meanoftbodygyrojerkstdz       Average     radians/s
tBodyAccMag-mean()	        tbodyaccmagmean	        meanoftbodyaccmagmean         Average     m/s^2^
tBodyAccMag-std()	          tbodyaccmagstd	        meanoftbodyaccmagstd          Average     m/s^2^     
tGravityAccMag-mean()	      tgravityaccmagmean	    meanoftgravityaccmagmean      Average     m/s^2^
tGravityAccMag-std()	      tgravityaccmagstd	      meanoftgravityaccmagstd       Average     m/s^2^
tBodyAccJerkMag-mean()	    tbodyaccjerkmagmean	    meanoftbodyaccjerkmagmean     Average     m/s^2^
tBodyAccJerkMag-std()	      tbodyaccjerkmagstd	    meanoftbodyaccjerkmagstd      Average     m/s^2^
tBodyGyroMag-mean()	        tbodygyromagmean	      meanoftbodygyromagmean        Average     radians/s
tBodyGyroMag-std()	        tbodygyromagstd	        meanoftbodygyromagstd         Average     radians/s
tBodyGyroJerkMag-mean()	    tbodygyrojerkmagmean	  meanoftbodygyrojerkmagmean    Average     radians/s
tBodyGyroJerkMag-std()	    tbodygyrojerkmagstd	    meanoftbodygyrojerkmagstd     Average     radians/s
fBodyAcc-mean()-X	          fbodyaccmeanx	          meanoffbodyaccmeanx           Average     m/s^2^
fBodyAcc-mean()-Y	          fbodyaccmeany	          meanoffbodyaccmeany           Average     m/s^2^
fBodyAcc-mean()-Z	          fbodyaccmeanz	          meanoffbodyaccmeanz           Average     m/s^2^
fBodyAcc-std()-X	          fbodyaccstdx        	  meanoffbodyaccstdx            Average     m/s^2^
fBodyAcc-std()-Y	          fbodyaccstdy	          meanoffbodyaccstdy            Average     m/s^2^
fBodyAcc-std()-Z	          fbodyaccstdz	          meanoffbodyaccstdz            Average     m/s^2^
fBodyAccJerk-mean()-X	      fbodyaccjerkmeanx	      meanoffbodyaccjerkmeanx       Average     m/s^2^
fBodyAccJerk-mean()-Y	      fbodyaccjerkmeany	      meanoffbodyaccjerkmeany       Average     m/s^2^
fBodyAccJerk-mean()-Z	      fbodyaccjerkmeanz	      meanoffbodyaccjerkmeanz       Average     m/s^2^
fBodyAccJerk-std()-X	      fbodyaccjerkstdx	      meanoffbodyaccjerkstdx        Average     m/s^2^
fBodyAccJerk-std()-Y	      fbodyaccjerkstdy	      meanoffbodyaccjerkstdy        Average     m/s^2^
fBodyAccJerk-std()-Z	      fbodyaccjerkstdz	      meanoffbodyaccjerkstdz        Average     m/s^2^
fBodyGyro-mean()-X	        fbodygyromeanx	        meanoffbodygyromeanx          Average     radians/s
fBodyGyro-mean()-Y	        fbodygyromeany	        meanoffbodygyromeany          Average     radians/s
fBodyGyro-mean()-Z	        fbodygyromeanz	        meanoffbodygyromeanz          Average     radians/s
fBodyGyro-std()-X	          fbodygyrostdx	          meanoffbodygyrostdx           Average     radians/s
fBodyGyro-std()-Y	          fbodygyrostdy	          meanoffbodygyrostdy           Average     radians/s
fBodyGyro-std()-Z	          fbodygyrostdz	          meanoffbodygyrostdz           Average     radians/s
fBodyAccMag-mean()	        fbodyaccmagmean	        meanoffbodyaccmagmean         Average     m/s^2^
fBodyAccMag-std()	          fbodyaccmagstd	        meanoffbodyaccmagstd          Average     m/s^2^
fBodyBodyAccJerkMag-mean()  fbodybodyaccjerkmagmean	meanoffbodybodyaccjerkmagmean Average     m/s^2^
fBodyBodyAccJerkMag-std()	  fbodybodyaccjerkmagstd	meanoffbodybodyaccjerkmagstd  Average     m/s^2^
fBodyBodyGyroMag-mean()	    fbodybodygyromagmean	  meanoffbodybodygyromagmean    Average     radians/s
fBodyBodyGyroMag-std()	    fbodybodygyromagstd	    meanoffbodybodygyromagstd     Average     radians/s
fBodyBodyGyroJerkMag-mean() fbodybodygyrojerkmagmeanmeanoffbodybodygyrojerkmagmeanAverage     radians/s
fBodyBodyGyroJerkMag-std()  fbodybodygyrojerkmagstd	meanoffbodybodygyrojerkmagstd Average     radians/s

I decided not to include the FreqMean variables since they were not mean or std of acceleration or gyro. 

Variables that were not used from the original dataset include:  
tBodyAcc-mad()-X  
tBodyAcc-mad()-Y  
tBodyAcc-mad()-Z  
tBodyAcc-max()-X  
tBodyAcc-max()-Y  
tBodyAcc-max()-Z  
tBodyAcc-min()-X  
tBodyAcc-min()-Y  
tBodyAcc-min()-Z  
tBodyAcc-sma()  
tBodyAcc-energy()-X  
tBodyAcc-energy()-Y  
tBodyAcc-energy()-Z  
tBodyAcc-iqr()-X  
tBodyAcc-iqr()-Y  
tBodyAcc-iqr()-Z  
tBodyAcc-entropy()-X  
tBodyAcc-entropy()-Y  
tBodyAcc-entropy()-Z  
tBodyAcc-arCoeff()-X,1  
tBodyAcc-arCoeff()-X,2  
tBodyAcc-arCoeff()-X,3  
tBodyAcc-arCoeff()-X,4  
tBodyAcc-arCoeff()-Y,1  
tBodyAcc-arCoeff()-Y,2  
tBodyAcc-arCoeff()-Y,3  
tBodyAcc-arCoeff()-Y,4  
tBodyAcc-arCoeff()-Z,1  
tBodyAcc-arCoeff()-Z,2  
tBodyAcc-arCoeff()-Z,3  
tBodyAcc-arCoeff()-Z,4  
tBodyAcc-correlation()-X,Y  
tBodyAcc-correlation()-X,Z  
tBodyAcc-correlation()-Y,Z  
tGravityAcc-mad()-X  
tGravityAcc-mad()-Y  
tGravityAcc-mad()-Z  
tGravityAcc-max()-X  
tGravityAcc-max()-Y  
tGravityAcc-max()-Z  
tGravityAcc-min()-X  
tGravityAcc-min()-Y  
tGravityAcc-min()-Z  
tGravityAcc-sma()  
tGravityAcc-energy()-X  
tGravityAcc-energy()-Y  
tGravityAcc-energy()-Z  
tGravityAcc-iqr()-X  
tGravityAcc-iqr()-Y  
tGravityAcc-iqr()-Z  
tGravityAcc-entropy()-X  
tGravityAcc-entropy()-Y  
tGravityAcc-entropy()-Z  
tGravityAcc-arCoeff()-X,1  
tGravityAcc-arCoeff()-X,2  
tGravityAcc-arCoeff()-X,3  
tGravityAcc-arCoeff()-X,4  
tGravityAcc-arCoeff()-Y,1  
tGravityAcc-arCoeff()-Y,2  
tGravityAcc-arCoeff()-Y,3  
tGravityAcc-arCoeff()-Y,4  
tGravityAcc-arCoeff()-Z,1  
tGravityAcc-arCoeff()-Z,2  
tGravityAcc-arCoeff()-Z,3  
tGravityAcc-arCoeff()-Z,4  
tGravityAcc-correlation()-X,Y  
tGravityAcc-correlation()-X,Z  
tGravityAcc-correlation()-Y,Z  
tBodyAccJerk-mad()-X  
tBodyAccJerk-mad()-Y  
tBodyAccJerk-mad()-Z  
tBodyAccJerk-max()-X  
tBodyAccJerk-max()-Y  
tBodyAccJerk-max()-Z  
tBodyAccJerk-min()-X  
tBodyAccJerk-min()-Y  
tBodyAccJerk-min()-Z  
tBodyAccJerk-sma()  
tBodyAccJerk-energy()-X  
tBodyAccJerk-energy()-Y  
tBodyAccJerk-energy()-Z  
tBodyAccJerk-iqr()-X  
tBodyAccJerk-iqr()-Y  
tBodyAccJerk-iqr()-Z  
tBodyAccJerk-entropy()-X  
tBodyAccJerk-entropy()-Y  
tBodyAccJerk-entropy()-Z  
tBodyAccJerk-arCoeff()-X,1  
tBodyAccJerk-arCoeff()-X,2  
tBodyAccJerk-arCoeff()-X,3  
tBodyAccJerk-arCoeff()-X,4  
tBodyAccJerk-arCoeff()-Y,1  
tBodyAccJerk-arCoeff()-Y,2  
tBodyAccJerk-arCoeff()-Y,3  
tBodyAccJerk-arCoeff()-Y,4  
tBodyAccJerk-arCoeff()-Z,1  
tBodyAccJerk-arCoeff()-Z,2  
tBodyAccJerk-arCoeff()-Z,3  
tBodyAccJerk-arCoeff()-Z,4  
tBodyAccJerk-correlation()-X,Y  
tBodyAccJerk-correlation()-X,Z   
tBodyAccJerk-correlation()-Y,Z  
tBodyGyro-mad()-X  
tBodyGyro-mad()-Y  
tBodyGyro-mad()-Z  
tBodyGyro-max()-X  
tBodyGyro-max()-Y  
tBodyGyro-max()-Z  
tBodyGyro-min()-X  
tBodyGyro-min()-Y  
tBodyGyro-min()-Z  
tBodyGyro-sma()  
tBodyGyro-energy()-X  
tBodyGyro-energy()-Y  
tBodyGyro-energy()-Z  
tBodyGyro-iqr()-X  
tBodyGyro-iqr()-Y  
tBodyGyro-iqr()-Z  
tBodyGyro-entropy()-X  
tBodyGyro-entropy()-Y  
tBodyGyro-entropy()-Z  
tBodyGyro-arCoeff()-X,1  
tBodyGyro-arCoeff()-X,2  
tBodyGyro-arCoeff()-X,3  
tBodyGyro-arCoeff()-X,4  
tBodyGyro-arCoeff()-Y,1  
tBodyGyro-arCoeff()-Y,2  
tBodyGyro-arCoeff()-Y,3  
tBodyGyro-arCoeff()-Y,4  
tBodyGyro-arCoeff()-Z,1  
tBodyGyro-arCoeff()-Z,2  
tBodyGyro-arCoeff()-Z,3  
tBodyGyro-arCoeff()-Z,4  
tBodyGyro-correlation()-X,Y  
tBodyGyro-correlation()-X,Z  
tBodyGyro-correlation()-Y,Z  
tBodyGyroJerk-mad()-X  
tBodyGyroJerk-mad()-Y   
tBodyGyroJerk-mad()-Z  
tBodyGyroJerk-max()-X  
tBodyGyroJerk-max()-Y  
tBodyGyroJerk-max()-Z  
tBodyGyroJerk-min()-X  
tBodyGyroJerk-min()-Y  
tBodyGyroJerk-min()-Z  
tBodyGyroJerk-sma()  
tBodyGyroJerk-energy()-X  
tBodyGyroJerk-energy()-Y  
tBodyGyroJerk-energy()-Z  
tBodyGyroJerk-iqr()-X  
tBodyGyroJerk-iqr()-Y  
tBodyGyroJerk-iqr()-Z  
tBodyGyroJerk-entropy()-X  
tBodyGyroJerk-entropy()-Y  
tBodyGyroJerk-entropy()-Z  
tBodyGyroJerk-arCoeff()-X,1  
tBodyGyroJerk-arCoeff()-X,2  
tBodyGyroJerk-arCoeff()-X,3  
tBodyGyroJerk-arCoeff()-X,4  
tBodyGyroJerk-arCoeff()-Y,1  
tBodyGyroJerk-arCoeff()-Y,2  
tBodyGyroJerk-arCoeff()-Y,3  
tBodyGyroJerk-arCoeff()-Y,4  
tBodyGyroJerk-arCoeff()-Z,1  
tBodyGyroJerk-arCoeff()-Z,2  
tBodyGyroJerk-arCoeff()-Z,3  
tBodyGyroJerk-arCoeff()-Z,4  
tBodyGyroJerk-correlation()-X,Y  
tBodyGyroJerk-correlation()-X,Z  
tBodyGyroJerk-correlation()-Y,Z   
tBodyAccMag-mad()  
tBodyAccMag-max()  
tBodyAccMag-min()  
tBodyAccMag-sma()  
tBodyAccMag-energy()  
tBodyAccMag-iqr()  
tBodyAccMag-entropy()  
tBodyAccMag-arCoeff()1  
tBodyAccMag-arCoeff()2  
tBodyAccMag-arCoeff()3  
tBodyAccMag-arCoeff()4  
tGravityAccMag-mad()  
tGravityAccMag-max()  
tGravityAccMag-min()  
tGravityAccMag-sma()  
tGravityAccMag-energy()  
tGravityAccMag-iqr()  
tGravityAccMag-entropy()  
tGravityAccMag-arCoeff()1  
tGravityAccMag-arCoeff()2  
tGravityAccMag-arCoeff()3  
tGravityAccMag-arCoeff()4  
tBodyAccJerkMag-mad()  
tBodyAccJerkMag-max()  
tBodyAccJerkMag-min()  
tBodyAccJerkMag-sma()  
tBodyAccJerkMag-energy()  
tBodyAccJerkMag-iqr()  
tBodyAccJerkMag-entropy()  
tBodyAccJerkMag-arCoeff()1  
tBodyAccJerkMag-arCoeff()2  
tBodyAccJerkMag-arCoeff()3  
tBodyAccJerkMag-arCoeff()4  
tBodyGyroMag-mad()  
tBodyGyroMag-max()  
tBodyGyroMag-min()  
tBodyGyroMag-sma()  
tBodyGyroMag-energy()  
tBodyGyroMag-iqr()  
tBodyGyroMag-entropy()  
tBodyGyroMag-arCoeff()1  
tBodyGyroMag-arCoeff()2  
tBodyGyroMag-arCoeff()3  
tBodyGyroMag-arCoeff()4  
tBodyGyroJerkMag-mad()  
tBodyGyroJerkMag-max()  
tBodyGyroJerkMag-min()  
tBodyGyroJerkMag-sma()  
tBodyGyroJerkMag-energy()  
tBodyGyroJerkMag-iqr()  
tBodyGyroJerkMag-entropy()  
tBodyGyroJerkMag-arCoeff()1  
tBodyGyroJerkMag-arCoeff()2  
tBodyGyroJerkMag-arCoeff()3  
tBodyGyroJerkMag-arCoeff()4  
fBodyAcc-mad()-X  
fBodyAcc-mad()-Y  
fBodyAcc-mad()-Z  
fBodyAcc-max()-X  
fBodyAcc-max()-Y  
fBodyAcc-max()-Z  
fBodyAcc-min()-X  
fBodyAcc-min()-Y  
fBodyAcc-min()-Z  
fBodyAcc-sma()  
fBodyAcc-energy()-X  
fBodyAcc-energy()-Y  
fBodyAcc-energy()-Z  
fBodyAcc-iqr()-X  
fBodyAcc-iqr()-Y  
fBodyAcc-iqr()-Z  
fBodyAcc-entropy()-X  
fBodyAcc-entropy()-Y  
fBodyAcc-entropy()-Z  
fBodyAcc-maxInds-X  
fBodyAcc-maxInds-Y  
fBodyAcc-maxInds-Z  
fBodyAcc-meanFreq()-X  
fBodyAcc-meanFreq()-Y  
fBodyAcc-meanFreq()-Z  
fBodyAcc-skewness()-X  
fBodyAcc-kurtosis()-X  
fBodyAcc-skewness()-Y  
fBodyAcc-kurtosis()-Y  
fBodyAcc-skewness()-Z  
fBodyAcc-kurtosis()-Z  
fBodyAcc-bandsEnergy()-1,8  
fBodyAcc-bandsEnergy()-9,16  
fBodyAcc-bandsEnergy()-17,24  
fBodyAcc-bandsEnergy()-25,32  
fBodyAcc-bandsEnergy()-33,40  
fBodyAcc-bandsEnergy()-41,48  
fBodyAcc-bandsEnergy()-49,56  
fBodyAcc-bandsEnergy()-57,64  
fBodyAcc-bandsEnergy()-1,16  
fBodyAcc-bandsEnergy()-17,32  
fBodyAcc-bandsEnergy()-33,48  
fBodyAcc-bandsEnergy()-49,64  
fBodyAcc-bandsEnergy()-1,24  
fBodyAcc-bandsEnergy()-25,48  
fBodyAcc-bandsEnergy()-1,8  
fBodyAcc-bandsEnergy()-9,16  
fBodyAcc-bandsEnergy()-17,24  
fBodyAcc-bandsEnergy()-25,32  
fBodyAcc-bandsEnergy()-33,40  
fBodyAcc-bandsEnergy()-41,48  
fBodyAcc-bandsEnergy()-49,56  
fBodyAcc-bandsEnergy()-57,64  
fBodyAcc-bandsEnergy()-1,16  
fBodyAcc-bandsEnergy()-17,32  
fBodyAcc-bandsEnergy()-33,48  
fBodyAcc-bandsEnergy()-49,64  
fBodyAcc-bandsEnergy()-1,24  
fBodyAcc-bandsEnergy()-25,48  
fBodyAcc-bandsEnergy()-1,8  
fBodyAcc-bandsEnergy()-9,16  
fBodyAcc-bandsEnergy()-17,24  
fBodyAcc-bandsEnergy()-25,32  
fBodyAcc-bandsEnergy()-33,40  
fBodyAcc-bandsEnergy()-41,48  
fBodyAcc-bandsEnergy()-49,56  
fBodyAcc-bandsEnergy()-57,64  
fBodyAcc-bandsEnergy()-1,16  
fBodyAcc-bandsEnergy()-17,32  
fBodyAcc-bandsEnergy()-33,48  
fBodyAcc-bandsEnergy()-49,64  
fBodyAcc-bandsEnergy()-1,24  
fBodyAcc-bandsEnergy()-25,48  
fBodyAccJerk-mad()-X  
fBodyAccJerk-mad()-Y  
fBodyAccJerk-mad()-Z  
fBodyAccJerk-max()-X  
fBodyAccJerk-max()-Y  
fBodyAccJerk-max()-Z  
fBodyAccJerk-min()-X  
fBodyAccJerk-min()-Y  
fBodyAccJerk-min()-Z  
fBodyAccJerk-sma()  
fBodyAccJerk-energy()-X  
fBodyAccJerk-energy()-Y  
fBodyAccJerk-energy()-Z  
fBodyAccJerk-iqr()-X  
fBodyAccJerk-iqr()-Y  
fBodyAccJerk-iqr()-Z  
fBodyAccJerk-entropy()-X  
fBodyAccJerk-entropy()-Y  
fBodyAccJerk-entropy()-Z  
fBodyAccJerk-maxInds-X  
fBodyAccJerk-maxInds-Y  
fBodyAccJerk-maxInds-Z  
fBodyAccJerk-meanFreq()-X  
fBodyAccJerk-meanFreq()-Y  
fBodyAccJerk-meanFreq()-Z  
fBodyAccJerk-skewness()-X  
fBodyAccJerk-kurtosis()-X  
fBodyAccJerk-skewness()-Y  
fBodyAccJerk-kurtosis()-Y  
fBodyAccJerk-skewness()-Z  
fBodyAccJerk-kurtosis()-Z  
fBodyAccJerk-bandsEnergy()-1,8  
fBodyAccJerk-bandsEnergy()-9,16  
fBodyAccJerk-bandsEnergy()-17,24  
fBodyAccJerk-bandsEnergy()-25,32  
fBodyAccJerk-bandsEnergy()-33,40  
fBodyAccJerk-bandsEnergy()-41,48  
fBodyAccJerk-bandsEnergy()-49,56  
fBodyAccJerk-bandsEnergy()-57,64  
fBodyAccJerk-bandsEnergy()-1,16  
fBodyAccJerk-bandsEnergy()-17,32  
fBodyAccJerk-bandsEnergy()-33,48  
fBodyAccJerk-bandsEnergy()-49,64  
fBodyAccJerk-bandsEnergy()-1,24  
fBodyAccJerk-bandsEnergy()-25,48  
fBodyAccJerk-bandsEnergy()-1,8  
fBodyAccJerk-bandsEnergy()-9,16  
fBodyAccJerk-bandsEnergy()-17,24  
fBodyAccJerk-bandsEnergy()-25,32  
fBodyAccJerk-bandsEnergy()-33,40  
fBodyAccJerk-bandsEnergy()-41,48  
fBodyAccJerk-bandsEnergy()-49,56  
fBodyAccJerk-bandsEnergy()-57,64  
fBodyAccJerk-bandsEnergy()-1,16  
fBodyAccJerk-bandsEnergy()-17,32  
fBodyAccJerk-bandsEnergy()-33,48  
fBodyAccJerk-bandsEnergy()-49,64  
fBodyAccJerk-bandsEnergy()-1,24  
fBodyAccJerk-bandsEnergy()-25,48  
fBodyAccJerk-bandsEnergy()-1,8  
fBodyAccJerk-bandsEnergy()-9,16  
fBodyAccJerk-bandsEnergy()-17,24  
fBodyAccJerk-bandsEnergy()-25,32  
fBodyAccJerk-bandsEnergy()-33,40  
fBodyAccJerk-bandsEnergy()-41,48  
fBodyAccJerk-bandsEnergy()-49,56  
fBodyAccJerk-bandsEnergy()-57,64  
fBodyAccJerk-bandsEnergy()-1,16  
fBodyAccJerk-bandsEnergy()-17,32  
fBodyAccJerk-bandsEnergy()-33,48  
fBodyAccJerk-bandsEnergy()-49,64  
fBodyAccJerk-bandsEnergy()-1,24  
fBodyAccJerk-bandsEnergy()-25,48  
fBodyGyro-mad()-X  
fBodyGyro-mad()-Y  
fBodyGyro-mad()-Z  
fBodyGyro-max()-X  
fBodyGyro-max()-Y  
fBodyGyro-max()-Z  
fBodyGyro-min()-X  
fBodyGyro-min()-Y  
fBodyGyro-min()-Z  
fBodyGyro-sma()  
fBodyGyro-energy()-X  
fBodyGyro-energy()-Y  
fBodyGyro-energy()-Z   
fBodyGyro-iqr()-X  
fBodyGyro-iqr()-Y  
fBodyGyro-iqr()-Z  
fBodyGyro-entropy()-X  
fBodyGyro-entropy()-Y  
fBodyGyro-entropy()-Z  
fBodyGyro-maxInds-X  
fBodyGyro-maxInds-Y  
fBodyGyro-maxInds-Z  
fBodyGyro-meanFreq()-X  
fBodyGyro-meanFreq()-Y  
fBodyGyro-meanFreq()-Z  
fBodyGyro-skewness()-X  
fBodyGyro-kurtosis()-X  
fBodyGyro-skewness()-Y  
fBodyGyro-kurtosis()-Y  
fBodyGyro-skewness()-Z  
fBodyGyro-kurtosis()-Z  
fBodyGyro-bandsEnergy()-1,8  
fBodyGyro-bandsEnergy()-9,16  
fBodyGyro-bandsEnergy()-17,24  
fBodyGyro-bandsEnergy()-25,32  
fBodyGyro-bandsEnergy()-33,40  
fBodyGyro-bandsEnergy()-41,48  
fBodyGyro-bandsEnergy()-49,56  
fBodyGyro-bandsEnergy()-57,64  
fBodyGyro-bandsEnergy()-1,16  
fBodyGyro-bandsEnergy()-17,32  
fBodyGyro-bandsEnergy()-33,48  
fBodyGyro-bandsEnergy()-49,64  
fBodyGyro-bandsEnergy()-1,24  
fBodyGyro-bandsEnergy()-25,48  
fBodyGyro-bandsEnergy()-1,8  
fBodyGyro-bandsEnergy()-9,16  
fBodyGyro-bandsEnergy()-17,24  
fBodyGyro-bandsEnergy()-25,32  
fBodyGyro-bandsEnergy()-33,40  
fBodyGyro-bandsEnergy()-41,48  
fBodyGyro-bandsEnergy()-49,56  
fBodyGyro-bandsEnergy()-57,64  
fBodyGyro-bandsEnergy()-1,16  
fBodyGyro-bandsEnergy()-17,32  
fBodyGyro-bandsEnergy()-33,48  
fBodyGyro-bandsEnergy()-49,64  
fBodyGyro-bandsEnergy()-1,24  
fBodyGyro-bandsEnergy()-25,48  
fBodyGyro-bandsEnergy()-1,8  
fBodyGyro-bandsEnergy()-9,16  
fBodyGyro-bandsEnergy()-17,24  
fBodyGyro-bandsEnergy()-25,32  
fBodyGyro-bandsEnergy()-33,40  
fBodyGyro-bandsEnergy()-41,48  
fBodyGyro-bandsEnergy()-49,56  
fBodyGyro-bandsEnergy()-57,64  
fBodyGyro-bandsEnergy()-1,16  
fBodyGyro-bandsEnergy()-17,32  
fBodyGyro-bandsEnergy()-33,48  
fBodyGyro-bandsEnergy()-49,64  
fBodyGyro-bandsEnergy()-1,24  
fBodyGyro-bandsEnergy()-25,48  
fBodyAccMag-mad()  
fBodyAccMag-max()  
fBodyAccMag-min()  
fBodyAccMag-sma()  
fBodyAccMag-energy()  
fBodyAccMag-iqr()  
fBodyAccMag-entropy()  
fBodyAccMag-maxInds  
fBodyAccMag-meanFreq()  
fBodyAccMag-skewness()  
fBodyAccMag-kurtosis()  
fBodyBodyAccJerkMag-mad()  
fBodyBodyAccJerkMag-max()  
fBodyBodyAccJerkMag-min()  
fBodyBodyAccJerkMag-sma()  
fBodyBodyAccJerkMag-energy()  
fBodyBodyAccJerkMag-iqr()  
fBodyBodyAccJerkMag-entropy()  
fBodyBodyAccJerkMag-maxInds  
fBodyBodyAccJerkMag-meanFreq()  
fBodyBodyAccJerkMag-skewness()  
fBodyBodyAccJerkMag-kurtosis  
fBodyBodyGyroMag-mad()  
fBodyBodyGyroMag-max()  
fBodyBodyGyroMag-min()  
fBodyBodyGyroMag-sma()  
fBodyBodyGyroMag-energy()  
fBodyBodyGyroMag-iqr()  
fBodyBodyGyroMag-entropy()  
fBodyBodyGyroMag-maxInds  
fBodyBodyGyroMag-meanFreq()  
fBodyBodyGyroMag-skewness()  
fBodyBodyGyroMag-kurtosis()  
fBodyBodyGyroJerkMag-mad()  
fBodyBodyGyroJerkMag-max()  
fBodyBodyGyroJerkMag-min()  
fBodyBodyGyroJerkMag-sma()  
fBodyBodyGyroJerkMag-energy()  
fBodyBodyGyroJerkMag-iqr()  
fBodyBodyGyroJerkMag-entropy()  
fBodyBodyGyroJerkMag-maxInds  
fBodyBodyGyroJerkMag-meanFreq()  
fBodyBodyGyroJerkMag-skewness()  
fBodyBodyGyroJerkMag-kurtosis()  
angle(tBodyAccMean,gravity)  
angle(tBodyAccJerkMean),gravityMean)  
angle(tBodyGyroMean,gravityMean)  
angle(tBodyGyroJerkMean,gravityMean)  
angle(X,gravityMean)  
angle(Y,gravityMean)  
angle(Z,gravityMean)  

